Study locations

### 2023-09-29 Scripts/1_Visualisation/Map_study_locations.Rmd
cleaning metaweb script

# Get all countries and transform to the same CRS
cntries <- gisco_get_countries(year = year_ref,
        resolution = 03) %>%
        st_transform(3035)

@@

colors <- c(
"#8AD69E", "#74C5CE",  "#FDE9DE",
"#45A631", "#95F7F0", "#CB53E1",
"#FE90BB", "#B187E1", "#F8A982", 
"#0075DC", "#993F00",  "#5EF1F2", 
"#005C31", "#74C5CE", "black", 
"lightblue",  "darkorange3","#8F7C00",
"#8F7C00","#8F7C00", "#9DCC00", 
"#C20088", "gold1","#FFA8BB",
"#426600","#94FFB5","#003380",  
"salmon", "palegreen","greenyellow",
"mediumaquamarine", "tomato", "orange", 
"blue", "black", "green",
"purple", "red")
#To generate more random colors 
#randomcoloR::distinctColorPalette(k = length(file_names), altCol = F, runTsne = T)

>>>>

# Get all countries and transform to the same CRS
cntries <- gisco_get_countries(region = "Europe", year = "2016") %>% 
          st_transform(3035)

cntries = sf::st_cast(cntries, "MULTIPOLYGON")

@@

colors <- c(
"#8AD69E", "#74C5CE",  "#FDE9DE",
"#45A631", "#95F7F0", "#CB53E1",
"#FE90BB", "#B187E1", "#F8A982", 
"#0075DC", "#993F00",  "#5EF1F2", 
"#005C31", "#74C5CE", "black", 
"lightblue",  "darkorange3","#8F7C00",
"#8F7C00","#8F7C00", "#9DCC00", 
"#C20088", "gold1","#FFA8BB",
"#426600","#94FFB5","#003380",  
"salmon", "palegreen","greenyellow",
"mediumaquamarine", "tomato", "orange", 
"blue", "black", "green",
"purple", "red", "gray")
#To generate more random colors 
#randomcoloR::distinctColorPalette(k = length(file_names), altCol = F, runTsne = T)
